Estimating the Initial Susceptible Fraction in Dengue Dynamics

### 2015-02-04 draft_lm1.tex
killing some white space
small edit to Table legend

Figure~\ref{fig:rtseries}  shows the $R_t$ series, according to 
(\ref{eq:Rtestimate})~\cite{nishiura} along with the confidence bands derived 
in this paper. 
It can be seen that the inter-epidemic periods are characterized by $R_t$ being 
indistinguishable from 1.
Due to the intrinsic variability of the \rr series, the examination of its 
credible intervals is essential to identify periods of sustained transmission.
The wider intervals between epidemics are due to the scarcity of cases during 
these periods.
The method to quantify uncertainty proposed here provides more conservative 
credibility intervals, and therefore offers protection against false alarms.

\begin{center}
\begin{figure}[!h]
 \centering
 \includegraphics[width=16cm]{./plots/rt_series.png}
 \caption{{\bf Estimated time-series for $R_t$, along with 95\% credible 
intervals.} Top panel show reported cases from which $R_t$ is estimated.
As expected, uncertainty about \rr is greater when the case counts are low, for 
instance in the period $2003$--$2006$, which represented a big hiatus between 
major epidemics.
The intrinsic variability of \rr can be used to inform the time-varying force 
of infection, since it reflects variation in the vector population and other 
environmental factors such as temperature and seasonal variation.}
\label{fig:rtseries}
\end{figure}
\end{center}

@@

\begin{table}[!ht]
\caption{
{\bf Median attack ratio and 95\% credibility intervals calculated according to 
(\ref{eq:AR2})}. 
Values are presented as percentage of total population. 
$^\dag$: Year corresponds to the start of the epidemic. 
Sometimes the peak of cases occur in the following year.
$^\ddag$: Susceptible fraction.}
\begin{center}
\begin{tabular}{c|c|c}
\hline
Year$^\dag$ & median Attack Ratio & $S_0^\ddag$ \\
\hline
1996 & 0.39 (0.17-0.54) & 0.00171(0.0012-0.0038)\\
1997 & 0.87 (0.74-0.87) & 0.00273(0.0027-0.0032)\\
1998 & 0.5 (0.49-0.5) & 0.00142(0.0014-0.0014)\\
1999 & 0.11 (0.037-0.2) & 0.00345(0.0018-0.01)\\
2000 & 0.25 (0.24-0.27) & 0.0155(0.015-0.016)\\
2001 & 0.48 (0.47-0.49) & 0.0495(0.048-0.051)\\
2005 & 0.15 (0.1-0.21) & 0.0147(0.01-0.021)\\
2006 & 0.11 (0.08-0.14) & 0.0281(0.022-0.037)\\
2007 & 0.15 (0.15-0.15) & 0.135(0.13-0.14)\\
2008 & 0.14 (0.031-0.31) & 0.00672(0.003-0.024)\\
2010 & 0.18 (0.17-0.19) & 0.0454(0.043-0.048)\\
2011 & 0.086 (0.082-0.094) & 0.215(0.2-0.23)\\
2012 & 0.14 (0.13-0.15) & 0.0621(0.058-0.068)\\
\hline
\end{tabular}
\end{center}
\label{tab:AR}
\end{table}

>>>>

Figure~\ref{fig:rtseries}  shows the $R_t$ series, according to 
(\ref{eq:Rtestimate})~\cite{nishiura} along with the confidence bands derived 
in this paper. 
It can be seen that the inter-epidemic periods are characterized by $R_t$ being 
indistinguishable from 1.
Due to the intrinsic variability of the \rr series, the examination of its 
credible intervals is essential to identify periods of sustained transmission.
The wider intervals between epidemics are due to the scarcity of cases during 
these periods.
The method to quantify uncertainty proposed here provides more conservative 
credibility intervals, and therefore offers protection against false alarms.
\begin{center}
\begin{figure}[!h]
 \centering
 \includegraphics[width=16cm]{./plots/rt_series.png}
 \caption{{\bf Estimated time-series for $R_t$, along with 95\% credible 
intervals.} Top panel show reported cases from which $R_t$ is estimated.
As expected, uncertainty about \rr is greater when the case counts are low, for 
instance in the period $2003$--$2006$, which represented a big hiatus between 
major epidemics.
The intrinsic variability of \rr can be used to inform the time-varying force 
of infection, since it reflects variation in the vector population and other 
environmental factors such as temperature and seasonal variation.}
\label{fig:rtseries}
\end{figure}
\end{center}

@@

\begin{table}[!ht]
\caption{
{\bf Median attack ratio and 95\% credibility intervals calculated according to 
(\ref{eq:AR2})}. 
Values are presented as percentage of total population. 
$^\dag$: Year corresponds to the start of the epidemic, however the peak of cases
may occur in the following year.
$^\ddag$: Susceptible fraction.
These results show considerable variation in AR between epidemics, consistent with
the accquiring and loss of serotype-specific immunity.}
\begin{center}
\begin{tabular}{c|c|c}
\hline
Year$^\dag$ & median Attack Ratio & $S_0^\ddag$ \\
\hline
1996 & 0.39 (0.17-0.54) & 0.00171(0.0012-0.0038)\\
1997 & 0.87 (0.74-0.87) & 0.00273(0.0027-0.0032)\\
1998 & 0.5 (0.49-0.5) & 0.00142(0.0014-0.0014)\\
1999 & 0.11 (0.037-0.2) & 0.00345(0.0018-0.01)\\
2000 & 0.25 (0.24-0.27) & 0.0155(0.015-0.016)\\
2001 & 0.48 (0.47-0.49) & 0.0495(0.048-0.051)\\
2005 & 0.15 (0.1-0.21) & 0.0147(0.01-0.021)\\
2006 & 0.11 (0.08-0.14) & 0.0281(0.022-0.037)\\
2007 & 0.15 (0.15-0.15) & 0.135(0.13-0.14)\\
2008 & 0.14 (0.031-0.31) & 0.00672(0.003-0.024)\\
2010 & 0.18 (0.17-0.19) & 0.0454(0.043-0.048)\\
2011 & 0.086 (0.082-0.094) & 0.215(0.2-0.23)\\
2012 & 0.14 (0.13-0.15) & 0.0621(0.058-0.068)\\
\hline
\end{tabular}
\end{center}
\label{tab:AR}
\end{table}
